Individual Rule Visualizations

### 2023-05-26 TestingPipeline/Scripts/individual_rule_set_visualizations.Rmd
Updated single rule rulesets.

ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity", color="black") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom",
    strip.background = element_rect(fill="white", color="grey"),
    strip.text = element_text(color="black")
  ) +
  scale_fill_manual(name="",
                     values = alpha(c(rev(pal_orange), pal_purple), 0.8)) +
  xlab("Ruleset") +
  ylab("Number of Sequences") + 
  facet_grid(rule_type~seqtype, scales = "free") 
```

>>>>

fig <- ggplot(viruses_long_scores, aes(y=n, x=rule_combination,
                   fill=viral_score)) +
  geom_bar(stat="identity", color="black") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom",
    strip.background = element_rect(fill="white", color="grey"),
    strip.text = element_text(color="black")
  ) +
  scale_fill_manual(name="Viral Score",
                     values = alpha(c(rev(RColorBrewer::brewer.pal(9,"Oranges")[4:7]),
                            RColorBrewer::brewer.pal(9,"Purples")[4:9] 
                            ), 0.8)) +
  xlab("Ruleset") +
  ylab("Proportion") + 
  facet_grid(rule_type~seqtype, scales = "free")

fig

ggsave(
  "../IntermediaryFiles/individual_tool_rulesets.png",
  plot = fig,
  scale = 1,
  width = 8,
  height = 4,
  units = c("in"),
  dpi = 300,
  limitsize = TRUE
)
```
